Robots Showing Emotions: Emotion Representation with no bio-inspired Body

### 2016-11-30 JournalInteractionStudies/Journal-AISB.tex
Minor changes based on the last comments

\abstract{Robots should be able to represent emotional states to interact with people as social agents. There are cases where robots cannot have bio-inspired bodies, for instance because the task to be performed requires a special shape, as in the case of home cleaners, package carriers, and many others. In these cases, emotional states have to be represented by exploiting movements of the body. In this paper, we present a set of case studies aimed to identify specific values to convey emotion though changes in linear and angular velocities, which might be applied on different non-bio-inspired bodies. The work originates from some of the most considered emotion expression theories and from emotion coding for people. We show that people can recognize some emotional expressions better than others, and we propose some directions to express emotions exploiting only bio-neutral movement.
}

>>>>

\abstract{Robots should be able to represent emotional states to interact with people as social agents. There are cases where robots cannot have bio-inspired bodies, for instance because the task to be performed requires a special shape, as in the case of home cleaners, package carriers, and many others. In these cases, emotional states have to be represented by exploiting movements of the body. In this paper, we present a set of case studies aimed at identifying specific values to convey emotion trough changes in linear and angular velocities, which might be applied on different non-anthropomorphic bodies. This work originates from some of the most considered emotion expression theories and from emotion coding for people. We show that people can recognize some emotional expressions better than others, and we propose some directions to express emotions exploiting only bio-neutral movement.
}

### 2016-11-30 JournalInteractionStudies/Parts/Emotion_Projection.tex
Minor changes based on the last comments

Regarding the movement or pose design, three major approaches could be found. In the first approach, actors are asked to perform different walks conveying emotions~\cite{Destephe2013b}. These movements are later reproduced with the robot, as closely as possible. A second approach is to ask some subjects to design the movements~\cite{Li2011}. The last approach is the empirical approach, where researches come with poses and movements based on their own experience~\cite{Canamero2010,Beck2010,Arras2012,Brown2014}. One major finding from diverse works~\cite{Canamero2010,Beck2010,Brown2014} is that moving the head up improved the identification of pride, happiness, and excitement. While moving the head down improved the identification of anger and sadness.

@@

It is important to mention the use of Laban’s Efforts~\cite{Laban1968} in the selection of the parameters in few works~\cite{BarakovaL10, Sharma2013}. Besides the fact that these works report that it was possible to convey emotions with non-human- or animal-like platforms, a relevant finding was the identification of the relationship between acceleration and speed with the arousal axis in the circumplex model of affect~\cite{Petta2010}.

@@

	\item \textit{Embodiment} tells if the robot is human-like, robot-like or neither of these two;

	\item \textit{Platform used} gives the name of the platform used on the study;

	\item \textit{Locomotion} gives information about the  displacement capabilities of the platform;

@@

	\item \textit{Emotion presentation} tells if a real robot was used in the study, or any other method;

	\item \textit{Emotions Implemented} gives the list of emotions presented to the subjects;

>>>>

Regarding the movement or pose design, three major approaches could be found. In the first approach, actors are asked to perform different walks conveying emotions~\cite{Destephe2013b}. These movements are later reproduced with the robot, as closely as possible. A second approach is to ask some subjects to design the movements~\cite{Li2011}. The last approach is the empirical approach, where researches come with poses and movements based on their own experience~\cite{Canamero2010,Beck2010,Arras2012,Brown2014}. One major finding from diverse works~\cite{Canamero2010,Beck2010,Brown2014} is that moving the head up improved the identification of \textit{pride}, \textit{happiness}, and \textit{excitement}. While moving the head down improved the identification of \textit{anger} and \textit{sadness}.

@@

It is important to mention the use of Laban's Efforts~\cite{Laban1968} in the selection of the parameters in few works~\cite{BarakovaL10, Sharma2013}. Besides the fact that these works report that it was possible to convey emotions with non-human- or animal-like platforms, a relevant finding was the identification of the relationship between acceleration and speed with the arousal axis in the circumplex model of affect~\cite{Petta2010}.

@@

	\item \textit{Embodiment} tells if the robot is human-like, robot-like or neither of these two.

	\item \textit{Platform used} gives the name of the platform used on the study.

	\item \textit{Locomotion} gives information about the  displacement capabilities of the platform.

@@

	\item \textit{Emotion presentation} tells if a real robot was used in the study, or any other method.

	\item \textit{Emotions Implemented} gives the list of emotions presented to the subjects.

### 2016-11-30 JournalInteractionStudies/Parts/case_studies.tex
Minor changes based on the last comments

In total, we did one pilot and four case studies using changes in linear and angular velocity, and oscillation angle to convey emotions. These features are depicted in Figure~\ref{fig:features}. The pilot was used to test the prototype and identify possible improvements. The feature values for the first case study were selected empirically and robot's movements were presented to participants. The results suggested that it was possible to convey some emotions, but it was decided to give a context to each emotion to test whether this could increase the recognition rate. A second case study was designed. Each emotion was presented to the participants in the context of a small scene, which was portrayed by the robot and a non professional human actor. The results suggested that showing the emotion in a context can improve the recognition of some emotions, so that the robotic emotional expression could be at least perceived as coherent with the context. However, the study of the impact of the actor and context were not in the aims of this research. To compare with literature on emotion projection, a third case study was implemented using parameters collected from diverse works, which encoded their emotion implementations using Laban's model. Having obtained similar results in both the first and third case studies, we decided to do an experiment to determine values that could better represent some emotions~\cite{Angel2017}. Thus, a final case study was done to cross-validate the so-far obtained findings.

@@

Each group of participants was exposed to three rounds, in each of which the robot was expressing a different emotion. The sequence of rounds was generated randomly without repeating any emotion in the same sequence. The subjects were asked to mark the emotion-related term that best described what they believed the robot was trying to express, selecting among a set of nine possible options: anger, curiosity, disgust, embarrassment, fear, happiness, sadness, pride, and neutral. The option to answer ``Unknown'' was also included. Although these ten options were enlisted, just the first eight emotions were implemented. To avoid that spectators could be influenced by previous trials, different emotions were shown to each group.

Additionally, every time that a new emotion was showed, the robot started $1.5 mts$ away from the participants, with its front facing them, as shown in  Figure~\ref{fig:setup}.

@@

It was decided to follow an empirical design for this case study, by considering the features that could be changed in the robot base and by composing them to express some basic emotions. The first implementations where tested and tuned basing on the emotions perceived by the researchers from the robot's movement. The features that could be easily perceived by the observer are summarized in table~\ref{table:features}, and each selected feature is described here below:

@@

\begin{table}[tbh]
\begin{center}
\small
\caption{Features that were presented in the first case study to the audience, and their respective values. Embarr. is Embarrassment and Asy. is Asymmetric.}
\label{table:features}
\begin{tabular}{|p{1.5 cm}|p{1.5 cm}|c|p{1.5 cm}|p{1.6 cm}|p{1.6 cm}|m{1.5 cm}|}
\hline 
\textbf{Emotion} & \textbf{Speed} & \textbf{Front/Back} & \textbf{Shoulder} & \textbf{Shoulder Amplitude} & \textbf{Angular Velocity} & \textbf{Body Rotation Amplitude} \\ 
\hline
Anger & Fast & No & Asy. & Medium & None & Very Small \\
\hline
Sadness & Very Slow & Yes-1 & Close-2 & None & Slow & Small \\
\hline
Fear & Normal Slow & Yes-2 & Close-2 + Asy. & Small & None & None \\ 
\hline
%Fear 2 & Slow & Yes-2 & Close-2 + Asymmetric & Small & None & Small \\
%\hline
Embarr. & Slow & No & Asy. & Large & Slow & Small \\
\hline
Happiness & Fast & No & Asy. & Medium & Fast & Small \\
\hline
Disgust & Slow & No & Few Asy. & Small & None & Very Small \\
\hline
Curiosity & Normal & No & Asy. & Medium & Slow & Large \\
\hline
Neutral & Normal & No & Asy. & Medium & None & None \\
\hline
\end{tabular}
\end{center}
\vspace{-0.5cm}
\end{table}

@@

There was no specific group size, since this was determined by the amount of people that got close to the booth at a given moment. Therefore, there were groups with just one person and others with 24 persons. The total amount of volunteers was 154: 55 males, 26 females, and 73 that did not specify their gender. The average age was 21.95 with a standard deviation of 12.26, minimum age was 5, maximum 62.

@@

In this second case study, the results were considerably better: four out of the nine showed emotion representations had a recognition percentage higher than 60\% (Anger, Happiness, Curiosity and Fear2). Another important point to highlight is that Sadness, Fear and Embarrassment were still perceived as different emotions. As it was done for the first case study, a Fisher's exact test and Holm-Bonferroni correction were applied for each possible combination of implemented emotions. The results suggest that no implementation was considered as similar to others by the participants, since for all we have $p-value<(\alpha = 0.05)$. 
Comparing the percentage from both the first two cases, it is possible to see that giving information about the context that produces the current emotional state of the robot improves the recognition of some emotions, but for others remains still low. Our hypothesis is that there must be a match between robot's movements with the given context and actor's performance to increase the recognition rate. If one or both do not fit participants' idea of the emotion, this one is not going to be recognized. To verify this, a comparison between the results obtained for each emotion in both cases doing a Fisher's exact test was done. The results suggest that implementations of Disgust ($p=0.088$), Fear ($p=0.206$) and Sadness ($p=0.269$) are perceived as the same in both cases, which correspond to the emotions with lower recognition rate. This opens the question about the influence that could have the human actor and the scene on the recognition rate. Although the study of this could be beneficial, it was decided to leave this to future work. Instead, a third case study was devised, where values presented in the literature for emotion expression in humans were adopted in the quest for more recognizable emotion expressions.

@@

In order to reduce the number of possible sequences, it was decided to implemented only four emotions. To select the emotions to be implemented, the \textit{circumplex model of affect} was adopted, as it was suggested by Sharma. The implemented emotions were: \textit{happiness} (I quadrant), \textit{anger} (II quadrant), \textit{sadness} (III quadrant), and \textit{content} (IV quadrant). To reduce the probability that the correct emotion could be selected by chance, four additional emotions were selected following the same selection procedure of the implemented ones, one from each quadrant. These emotions were: \textit{frustration}, \textit{boredom}, \textit{astonishment}, and \textit{tiredness}. The final questionnaire had nine possibilities (eight emotions and ``Unknown''), and was better founded on psychological theory than the previous ones.

@@

	\item Anger: the strong force required by Laban was interpreted as a high speed and then a sudden drop, thus it was decided to have a velocity of $500mm/sec$ for $50mm$ and then a velocity of $300mm/sec$. An oscillation during the whole trajectory was also added; that was between [0.086, -0.086] radians with an angular velocity of $3.5 rad/sec$.

	\item Happiness: as in Anger, for the first $50mm$ the velocity was $500mm/sec$, then it went down to $400mm/sec$ for another $50mm$, and then up again to $800mm/sec$ for the rest of the movement. 
	An oscillation between [0.26, -0.26] radians with an angular velocity of $3rad/sec$ was also added.

	\item Sadness: the required "low energy" was interpreted as low speed and then slowing down the pace, thus a velocity of $150mm/sec$ was used for the first $200mm$, a velocity $250mm/sec$ for the next $200mm$, and for the rest a velocity of $300mm/sec$. This emotion expression did not include any angular rotation.

	\item Content: the velocity was $150mm/sec$ for the first $200mm$, then $300mm/sec$ for the rest. The maximum and minimum angle of oscillation were [0.175, -0.175] with angular velocity of $0.17rad/sec$
\end{itemize}

@@

From the open questionnaire, different terms to describe both emotions and mental states were obtained. The results are reported in table~\ref{table:open_questionnaire}. In order to reduce the quantity of terms, words that have a similar meaning were grouped, for example words such as Fear, Terror, Scared, and Worried were grouped under the label Fear. Also, three out of four emotions (Anger, Happiness and Sadness) were at least once listed correctly. Sadness and Content were mostly perceived as Fear, being reported 31\% and 28\% of the time, respectively.

@@

	\item The language richness to refer to emotions and the vague definition of emotions let people to use words that could not be directly associated to a specific emotion.

	\item The movements that could be designed as emotional are also associated to mental states attributed to the robot. This is evident in the words obtained from the presentation of four ``emotional'' movements, such as: cold (referring that the robot was feeling cold), tenderness, shyness, power, hurry, looking for something, he wants something, enthusiasm, sympathy, vanity, and obedience.

@@

\begin{table}[h]
\centering
\small
\caption{Answers obtained from the closed list group in the third case study.}
		\label{table:result_list_emotions}
		\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
			\hline	
\rotatebox{90}{\backslashbox{Presented}{Reported}}&
\rotatebox{90}{Anger}&
\rotatebox{90}{ Happiness} &
\rotatebox{90}{Sadness}&
\rotatebox{90}{Content}&
\rotatebox{90}{Frustration}&
\rotatebox{90}{Boredom}&
\rotatebox{90}{Astonishment}&
\rotatebox{90}{Tiredness}&
\rotatebox{90}{Unknown}&
\rotatebox{90}{Total}\\	
			\hline
				Anger&19&8&1&5&7&2&5&1&0&48\\
			\hline
				Happiness&18&19&0&9&5&1&5&1&0&58\\
			\hline
				Sadness&1&9&12&2&4&5&7&6&0&46\\
			\hline
				Content&2&8&7&4&6&8&5&10&0&50\\	
			\hline	
			\end{tabular}
\end{table}

An analysis was done for each emotion, therefore it was created a contingency matrix such as it was done in the first case study.
Additional two confusion matrices were created: one merging the results from all high (\textit{anger}, \textit{happiness}, \textit{frustration} and \textit{astonishment}) and low (\textit{sadness}, \textit{content}, \textit{boredom}, and \textit{tiredness}) arousal emotions; the other matrix merges the results of positive (\textit{happiness}, \textit{content}, \textit{astonishment}, and \textit{tiredness}) and negative (\textit{anger}, \textit{frustration}, \textit{boredom}, and \itemsadness) emotions. For each of these tables, the positive predictive value, accuracy and a Pearson's $\chi^2$ were calculated. The results are shown in table~\ref{table:Precision}. They show that there is significant evidence to conclude that \textit{anger}, \textit{\textit{happiness}}, and \textit{sadness} could be perceived, while the implementation of \textit{content} was not significantly recognized. Moreover, high and low arousal are perceived as different, but this is not the case for positive and negative valence.

@@

To analyse whether any emotion expression was misinterpreted with any other, a Fisher's exact test and Holm-Bonferroni correction were applied for each possible combination of the implemented emotions, which gives a total of seven combinations.  
The results suggest that the implementations of \textit{anger} and \textit{happiness} ($p-value=0.9$), and, respectively, \textit{sadness} and \textit{content} ($p-value=0.9$) are interpreted as similar, while all the other emotion expressions are distinguished from each other.

From the results of both questionnaires, we can say that \textit{anger} and \textit{happiness} were confused, as well \textit{sadness} and \textit{content}. \textit{Fear} was selected when the two emotions with low arousal (\textit{sadness} and \textit{content}) were shown. These results show that velocity plays a role to elicit emotions, but that it is necessary to add additional features (e.g., changes on body shape) to increase the discrimination among low and high arousal emotions, respectively. Having obtained similar results in the first and third case studies, we decided to design an experiment to identify values that could lead to better expressions of some emotions~\cite{Angel2017}.

@@

From the results obtained on our experiments, we selected two emotion implementations with the higher Krippendorff's alpha coefficient~\cite{Klaus2007} and mean for each emotion studied in an experiment done after the third case study. As in the previous case studies, a questionnaire was used. This time, the emotions listed in the questionnaire were the same used during the experiment: \textit{anger}, \textit{fear}, \textit{sadness}, and \textit{happiness}. Moreover, two mental states were added: \textit{excited} and \textit{tender}, which correspond to high and low arousal, respectively. As it was done in the previous cases, the questionnaire included the option ''unknown''. Although the platform used was the last version (Figure~\ref{fig:triskar-third-design}), the upper part was cut off to allow comparisons with the platform used in the other experiments. The case study set up could be seen in Figure~\ref{fig:setup_fourth}.

@@

It could be observed that both implementations of \textit{happiness} are confused with \textit{anger} and \textit{excitement}, as it could have been expected. The first implementation of \textit{anger} was recognized as \textit{anger} just 10\% of the times, but it was confused as \textit{excitement} 42\%. On the other hand, the second implementation showed an improvement from 10\% to 38\% on recognition. 
This implementation was perceived also as \textit{happiness}, \textit{fear} and \textit{excitement} by 18\%, 17\%, and 17\%, respectively. Both implementations of \textit{fear} have a high level of recognition 54\% and 50\% and are mostly confused with \textit{excitement}, 17\% for the first implementation and 27\% for the second implementation. Lastly, the first implementation of \textit{sadness} was confused with \textit{fear} and \textit{tenderness} by 26\% and 24\%, respectively. The second implementation was confused again with \textit{fear} and \textit{tenderness} by 19\% and 19\%, respectively.

To verify these misinterpretations among the implemented emotions, a Fisher's exact test and Holm-Bonferroni correction were applied for 10 different combinations. The results are shown in Table~\ref{table:result_compare_fourth}. As the results suggest, the two implementations of \textit{anger} are the only ones that were considered as different from all others.

@@

As it was done in the previous case studies a contingency matrix was computed for each emotion. 
For each of these tables, the positive predictive value, accuracy and a Pearson's $\chi^2$ were calculated. The results are shown in table~\ref{table:Precision2}. They show that there is significant evidence to conclude that one implementation of \textit{anger}, and both those of \textit{fear} and \textit{sadness} could be perceived correctly, while both implementations of \textit{happiness} and the other one of \textit{anger} were not.

>>>>

In total, we did one pilot and four case studies using changes in linear and angular velocity, and oscillation angle to convey emotions. These features are depicted in Figure~\ref{fig:features}. The pilot was used to test the prototype and identify possible improvements. The feature values for the first case study were selected empirically and robot's movements were presented to participants. The results suggested that it was possible to convey some emotions, but it was decided to give a context to each emotion to test whether this could increase the recognition rate. A second case study was designed. Each emotion was presented to the participants in a context of a small scene, which was portrayed by the robot and a non-professional human actor. The results suggested that showing the emotion in a context can improve the recognition of some emotions, so that the robotic emotional expression could be at least perceived as coherent with the context. However, the study of the impact of the actor and context were not in the aims of this research. To compare with literature on emotion projection, a third case study was implemented using parameters collected from diverse works, which encoded their emotion implementations using Laban's model. Having obtained similar results in both first and third case studies, we decided to do an experiment to determine values that could better represent some emotions~\cite{Angel2017}. Thus, a final case study was done to cross-validate the so-far obtained findings.

@@

Each group of participants was exposed to three rounds, in each of which the robot was expressing a different emotion. The sequence of rounds was generated randomly without repeating any emotion in the same sequence. The subjects were asked to mark the emotion-related term that best described what they believed the robot was trying to express, selecting among a set of nine possible options: \textit{anger}, \textit{curiosity}, \textit{disgust}, \textit{embarrassment}, \textit{fear}, \textit{happiness}, \textit{sadness}, \textit{pride}, and \textit{neutral}. The option to answer ``Unknown'' was also included. Although these ten options were enlisted, just the first eight emotions were implemented. To avoid that spectators could be influenced by previous trials, different emotions were shown to each group.

Additionally, every time that a new emotion was showed, the robot started $1.5 m$ away from the participants, with its front facing them, as shown in  Figure~\ref{fig:setup}.

@@

It was decided to follow an empirical design for this case study, by considering features that could be changed in the robot base and by composing them to express some basic emotions. The first implementations were tested and tuned basing on the emotions perceived by us from the robot's movement. The features that could be easily perceived are summarized in table~\ref{table:features}, and each selected feature is described here below:

@@

\begin{table}[tbh]
\begin{center}
\small
\caption{Features that were presented in the first case study to the audience, and their respective values. Embarr. is Embarrassment and Asy. is Asymmetric.}
\label{table:features}
\begin{tabular}{|p{1.5 cm}|p{1.5 cm}|c|p{1.5 cm}|p{1.6 cm}|p{1.6 cm}|m{1.5 cm}|}
\hline 
\textbf{Emotion} & \textbf{Speed} & \textbf{Front/Back} & \textbf{Shoulder} & \textbf{Shoulder Amplitude} & \textbf{Angular Velocity} & \textbf{Body Rotation Amplitude} \\ 
\hline
Anger & Fast & No & Asy. & Medium & None & Very Small \\
\hline
Sadness & Very Slow & Yes-1 & Close-2 & None & Slow & Small \\
\hline
Fear & Normal Slow & Yes-2 & Close-2 + Asy. & Small & None & None \\ 
\hline
Embarr. & Slow & No & Asy. & Large & Slow & Small \\
\hline
Happiness & Fast & No & Asy. & Medium & Fast & Small \\
\hline
Disgust & Slow & No & Few Asy. & Small & None & Very Small \\
\hline
Curiosity & Normal & No & Asy. & Medium & Slow & Large \\
\hline
Neutral & Normal & No & Asy. & Medium & None & None \\
\hline
\end{tabular}
\end{center}
\vspace{-0.5cm}
\end{table}

@@

There was no specific group size, since this was determined by the amount of people that got close to the both at a given moment. Therefore, there were groups with just one person and others with 24 persons. The total amount of volunteers was 154: 55 males, 26 females, and 73 that did not specify their gender. The average age was 21.95 with a standard deviation of 12.26, minimum age was 5, maximum 62.

@@

In this second case study, the results were considerably better: four out of the nine showed emotion representations had a recognition percentage higher than 60\% (\textit{Anger}, \textit{Happiness}, \textit{Curiosity} and \textit{Fear2}). Another important point to highlight is that \textit{Sadness}, \textit{Fear} and \textit{Embarrassment} were still perceived as different emotions. As it was done for the first case study, a Fisher's exact test and Holm-Bonferroni correction were applied for each possible combination of implemented emotions. The results suggest that no implementation was considered as similar by the participants, since for all we have $p-value<(\alpha = 0.05)$. 
Comparing the percentage from both the first two cases, it is possible to see that giving information about the context that produces the current emotional state of the robot improves the recognition of some emotions, but for others remains still low. Our hypothesis is that there must be a match between robot's movements with the given context and actor's performance to increase the recognition rate. If one or both do not fit participants' idea of the emotion, this one is not going to be recognized. To verify this, a comparison between the results obtained for each emotion in both cases doing a Fisher's exact test was done. The results suggest that implementations of \textit{Disgust} ($p=0.088$), \textit{Fear} ($p=0.206$) and \textit{Sadness} ($p=0.269$) are perceived as the same in both cases, which correspond to the emotions with lower recognition rate. This opens the question about the influence that could have the human actor and the scene on the recognition rate. Although the study of this could be beneficial, it was decided to leave this to future work. Instead, a third case study was devised, where values presented in the literature for emotion expression in humans were adopted in the quest for more recognizable emotion expressions.

@@

In order to reduce the number of possible sequences, it was decided to implemented only four emotions. To select the emotions to be implemented, the \textit{circumplex model of affect} was adopted, as it was suggested by Sharma. The implemented emotions were: \textit{Happiness} (I quadrant), \textit{Anger} (II quadrant), \textit{Sadness} (III quadrant), and \textit{Content} (IV quadrant). To reduce the probability that the correct emotion could be selected by chance, four additional emotions were selected following the same selection procedure of the implemented ones, one from each quadrant. These emotions were: \textit{Frustration}, \textit{Boredom}, \textit{Astonishment}, and \textit{Tiredness}. The final questionnaire had nine possibilities (eight emotions and ``Unknown''), and was better founded on psychological theory than the previous ones.

@@

	\item \textit{Anger}: the strong force required by Laban was interpreted as a high speed and then a sudden drop, thus it was decided to have a velocity of $500mm/sec$ for $50mm$ and then a velocity of $300mm/sec$. An oscillation during the whole trajectory was also added; that was between [0.086, -0.086] radians with an angular velocity of $3.5 rad/sec$.

	\item \textit{Happiness}: as in \textit{Anger}, for the first $50mm$ the velocity was $500mm/sec$, then it went down to $400mm/sec$ for another $50mm$, and then up again to $800mm/sec$ for the rest of the movement. 
	An oscillation between [0.26, -0.26] radians with an angular velocity of $3rad/sec$ was also added.

	\item \textit{Sadness}: the required "low energy" was interpreted as low speed and then slowing down the pace, thus a velocity of $150mm/sec$ was used for the first $200mm$, a velocity $250mm/sec$ for the next $200mm$, and for the rest a velocity of $300mm/sec$. This emotion expression did not include any angular rotation.

	\item \textit{Content}: the velocity was $150mm/sec$ for the first $200mm$, then $300mm/sec$ for the rest. The maximum and minimum angle of oscillation were [0.175, -0.175] with angular velocity of $0.17rad/sec$
\end{itemize}

@@

From the open questionnaire, different terms to describe both emotions and mental states were obtained. The results are reported in table~\ref{table:open_questionnaire}. In order to reduce the quantity of terms, words that have a similar meaning were grouped, for example words such as Fear, Terror, Scared, and Worried were grouped under the label \textit{Fear}. Also, three out of four emotions (\textit{Anger}, \textit{Happiness} and \textit{Sadness}) were at least once listed correctly. \textit{Sadness} and \textit{Content} were mostly perceived as \textit{Fear}, being reported 31\% and 28\% of the time, respectively.

@@

	\item Language richness to refer to emotions and the vague definition of emotions let people to use words that could not be directly associated to a specific emotion.

	\item Movements that could be designed as emotional are also associated to mental states attributed to the robot. This is evident in the words obtained from the presentation of four ``emotional'' movements, such as: cold (referring that the robot was feeling cold), tenderness, shyness, power, hurry, looking for something, he wants something, enthusiasm, sympathy, vanity, and obedience.

@@

\begin{table}[h]
\centering
\small
\caption{Answers obtained from the closed list group in the third case study.}
		\label{table:result_list_emotions}
		\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
			\hline	
\backslashbox{Presented}{Reported}&
\rotatebox{90}{Anger}&
\rotatebox{90}{ Happiness} &
\rotatebox{90}{Sadness}&
\rotatebox{90}{Content}&
\rotatebox{90}{Frustration}&
\rotatebox{90}{Boredom}&
\rotatebox{90}{Astonishment}&
\rotatebox{90}{Tiredness}&
\rotatebox{90}{Unknown}&
\rotatebox{90}{Total}\\	
			\hline
				Anger&19&8&1&5&7&2&5&1&0&48\\
			\hline
				Happiness&18&19&0&9&5&1&5&1&0&58\\
			\hline
				Sadness&1&9&12&2&4&5&7&6&0&46\\
			\hline
				Content&2&8&7&4&6&8&5&10&0&50\\	
			\hline	
			\end{tabular}
\end{table}

An analysis was done for each emotion, therefore it was created a contingency matrix such as it was done in the first case study.
Additionally, two confusion matrices were created: one merging the results from all high (\textit{Anger}, \textit{Happiness}, \textit{Frustration} and \textit{Astonishment}) and low (\textit{Sadness}, \textit{Content}, \textit{Boredom}, and \textit{Tiredness}) arousal emotions; the other matrix merges the results of positive (\textit{Happiness}, \textit{Content}, \textit{Astonishment}, and \textit{Tiredness}) and negative (\textit{Anger}, \textit{Frustration}, \textit{Boredom}, and \textit{Sadness}) emotions. For each of these tables, the positive predictive value, accuracy and a Pearson's $\chi^2$ were calculated. The results are shown in table~\ref{table:Precision}. They show that there is significant evidence to conclude that \textit{Anger}, \textit{\textit{Happiness}}, and \textit{Sadness} could be perceived, while the implementation of \textit{Content} was not significantly recognized. Moreover, high and low arousal are perceived as different, but this is not the case for positive and negative valence.

@@

To analyse whether any emotion expression was misinterpreted among them, a Fisher's exact test and Holm-Bonferroni correction were applied for each possible combination of the implemented emotions, which gives a total of seven combinations.  
The results suggest that the implementations of \textit{Anger} and \textit{Happiness} ($p-value=0.9$), and, respectively, \textit{Sadness} and \textit{Content} ($p-value=0.9$) are interpreted as similar, while all the other emotion expressions are distinguished from each other.

From the results of both questionnaires, we can say that \textit{Anger} and \textit{Happiness} were confused, as well \textit{Sadness} and \textit{Content}. \textit{Fear} was selected when the two emotions with low arousal (\textit{Sadness} and \textit{Content}) were shown. These results show that velocity plays a role to elicit emotions, but that it is necessary to add additional features (e.g., changes on body shape) to increase the discrimination among low and high arousal emotions, respectively. Having obtained similar results in the first and third case studies, we decided to design an experiment to identify values that could lead to better expressions of some emotions~\cite{Angel2017}.

@@

From the results obtained on our experiments, we selected two emotion implementations with the higher Krippendorff's alpha coefficient~\cite{Klaus2007} and mean for each emotion studied in an experiment done after the third case study. As in the previous case studies, a questionnaire was used. This time, the emotions listed in the questionnaire were the same used during the experiment: \textit{Anger}, \textit{Fear}, \textit{Sadness}, and \textit{Happiness}. Moreover, two mental states were added: \textit{Excited} and \textit{Tender}, which correspond to high and low arousal, respectively. As it was done in the previous cases, the questionnaire included the option ''unknown''. Although the platform used was the last version (Figure~\ref{fig:triskar-third-design}), the upper part was cut off to allow comparisons with the platform used in the other experiments. The case study set up could be seen in Figure~\ref{fig:setup_fourth}.

@@

It could be observed that both implementations of \textit{Happiness} are confused with \textit{Anger} and \textit{Excitement}, as it could have been expected. The first implementation of \textit{Anger} was recognized as \textit{Anger} just 10\% of the times, but it was confused as \textit{Excitement} 42\%. On the other hand, the second implementation showed an improvement from 10\% to 38\% on recognition. 
This implementation was perceived also as \textit{Happiness}, \textit{Fear} and \textit{Excitement} by 18\%, 17\%, and 17\%, respectively. Both implementations of \textit{Fear} have a high level of recognition 54\% and 50\% and are mostly confused with \textit{Excitement}, 17\% for the first implementation and 27\% for the second implementation. Lastly, the first implementation of \textit{Sadness} was confused with \textit{Fear} and \textit{Tenderness} by 26\% and 24\%, respectively. The second implementation was confused again with \textit{Fear} and \textit{Tenderness} by 19\% and 19\%, respectively.

To verify these misinterpretations among the implemented emotions, a Fisher's exact test and Holm-Bonferroni correction were applied to 10 different combinations. The results are shown in Table~\ref{table:result_compare_fourth}. As results suggest, two implementations of \textit{Anger} are the only ones that were considered as different from all others.

@@

As it was done in the previous case studies a contingency matrix was computed for each emotion. 
For each of these tables, the positive predictive value, accuracy and a Pearson's $\chi^2$ were calculated. The results are shown in table~\ref{table:Precision2}. They show that there is significant evidence to conclude that one implementation of \textit{Anger}, and both those of \textit{Fear} and \textit{Sadness} could be perceived correctly, while both implementations of \textit{Happiness} and the other one of \textit{Anger} were not.

### 2016-11-30 JournalInteractionStudies/Parts/conclusions.tex
Minor changes based on the last comments

	\item The change in the body shape increases the emotion identification rate of the observers. However, the characteristics that should be changed to increment the emotions perception are still to be investigated.

@@

	\item Emotions come as a reaction to an event. Therefore, just showing uncorrelated movements to the participants is not going to support the study of the expression of all the emotions. For example, the emotional expression of \textit{fear} was well perceived by the participants when the robot moved far from them, as they felt they were inducing it.

>>>>

	\item Change in the body shape increases the emotion identification rate of the observers. However, the characteristics that should be changed to increment the emotions perception are still to be investigated.

@@

	\item Emotions come as a reaction to an event. Therefore, just showing uncorrelated movements to the participants is not going to support the study of the expression of all the emotions. For example, the emotional expression of \textit{Fear} was well perceived by the participants when the robot moved far from them, as they felt they were inducing it.
